### 2013-02-11 Docs/FAQ/faq.tex

>>>>

\item {\em Why does ``checkerboarding'' appear in the velocity field,
especially in regions where the flow is stagnant?}

Checkerboarding can arise from the projection---it doesn't see that
mode (because it is an approximate projection) so it is unable to
remove it.  This allows the pattern to slowly build up.  There are
filtering techniques that can be used to remove these modes, but
they are not implemented in \maestro.
